Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-08-13 GWLDCII.tex
still tweaking 3.15

Now repeat the argument above with $p_s$ in place of $p_r$: if the other end of $p_s$ lands on an edge between $q$ and $j_m$ then we have $q \in \cP_{m-1}$ as above; if not then there exists some $p_t \in Q_{l-3}$ with $p_s$ supported on $I_i(p_t)$ and \hlfix{$I_i(p_t) <_i I_i(p_r)$}{$I_i(p_t) <_i I_i(p_s)<_i I_i(p_s)$? Or is the implication clear enough not to be mentioned}\note{Nope: we just need $<_i I_i(p_r)$. $I_i(p_t) <_i I_i(p_r)$ certainly isn't obvious and may not be true}. {\color{violet} May not be necessary, but I think highlighted tex follows from "Now repeat the argument...." \begin{enumerate}\item If $V(p_r) \in [a_r-1, j_m]$ (other end closer to $j_m$) then $q$ inside $p_r$ in $a_r-1$ order. \item Else, $V(p_r) \in [i, a_r+1]$ (Maybe $[i-1, a_r +1]$?). (Main point is that other end closer to $i$) Either way,  admissibility implies that $a_s < a_r$ \item Now we repeat. Either  $V(p_s) \in [a_s-1, j_m]$ then $q$ inside $p_s$ in $a_s-1$ order and we are done \item Else, $V(p_s) \in [i, a_s+1]$ (Maybe $[i-1, a_s +1]$?). Either way, admissibility implies that $a_t < a_s$ and we've already established $a_s < a_r$ \end{enumerate} We don't have to include this argument. It may be totally unnecessary. But I want to make certain that I'm not missing anything.}  Since there are finitely many steps this process can take before reaching $Q_0$, and any $p_* \in Q_0  = \Prop(j_m)$ has $j_m$ in its support by definition, this argument eventually terminates with the construction of a propagator constraining the positioning of $q$ as required. This completes the induction step, and hence the proof.\end{proof}

>>>>

Now repeat the argument above with $p_s$ in place of $p_r$: if the other end of $p_s$ lands on an edge between $q$ and $j_m$ then we have $q \in \cP_{m-1}$ as above; if not then there exists some $p_t \in Q_{l-3}$ with $p_s$ supported on $I_i(p_t)$ and $q$ on the inside of $p_t$ in the $a_t-1$ order. Thereofore \hlfix{$I_i(p_t) <_i I_i(p_r)$}{$I_i(p_t) <_i I_i(p_s)<_i I_i(p_s)$? Or is the implication clear enough not to be mentioned}\note{Nope: we just need $<_i I_i(p_r)$. $I_i(p_t) <_i I_i(p_r)$ certainly isn't obvious and may not be true}. {\color{violet} May not be necessary, but I think highlighted tex follows from "Now repeat the argument...." \begin{enumerate}\item If $V(p_r) \in [a_r-1, j_m]$ (other end closer to $j_m$) then $q$ inside $p_r$ in $a_r-1$ order. \item Else, $V(p_r) \in [i, a_r+1]$ (Maybe $[i-1, a_r +1]$?). (Main point is that other end closer to $i$) Either way,  admissibility implies that $a_s < a_r$ \item Now we repeat. Either  $V(p_s) \in [a_s-1, j_m]$ then $q$ inside $p_s$ in $a_s-1$ order and we are done \item Else, $V(p_s) \in [i, a_s+1]$ (Maybe $[i-1, a_s +1]$?). Either way, admissibility implies that $a_t < a_s$ and we've already established $a_s < a_r$ \end{enumerate} We don't have to include this argument. It may be totally unnecessary. But I want to make certain that I'm not missing anything.}  Since there are finitely many steps this process can take before reaching $Q_0$, and any $p_* \in Q_0  = \Prop(j_m)$ has $j_m$ in its support by definition, this argument eventually terminates with the construction of a propagator constraining the positioning of $q$ as required. This completes the induction step, and hence the proof.\end{proof}
